# Variable names, function names, object names

> Be consistent! Seriously...

There are no best way to write your variables, objects or function names but there are definitely worth ways: when you're inconsistent. The idea here, for making your code easy and nice to read (for yourself and others) is to choose a coding style and to stick to it. They are a couple of "standard" styles (e.g. the [Google one](https://google.github.io/styleguide/Rguide.xml)) but they are by no mean the norm and you don't have to follow them **as long as you a consistent style**.

For example, this is my (Thomas) style (by no means the best one).

## Comments

I always use two hashes for a code comment, i.e. a comment that describes what the code does:

```{r, eval = FALSE}
## This prints the value 1 then 2
print(1)
print(2)
```

For code that is commented out, i.e. not run for any reason, I use a single hash:

```{r, eval = FALSE}
## This prints the value 1 then 2
print(1)
# print(2)
```

This can be useful for some debug section, especially when using `...` arguments like:

```{r, eval = FALSE}
## Some debug single hash use
plot(1, 1, ...)
# plot(1, 1) ; warning("DEBUG")
```

Running the line `plot(1, 1, ...)` will throw an error so it's annoying, however, it's possible to run the "simplified" version by just un-commenting the `# plot(1, 1) ; warning("DEBUG")` line. The `warning("DEBUG")` part will remind you that you forgot to comment it back if you end up running the whole function.

Finally, for specific comments meant to the users, I will use the following format:

```{r}
#TODO: adding more interesting stuff to this guideline
#TG: hey future me, can you make this tutorial more interesting?
```

Where `#TODO` is a suggestion for a future version and `#TG` (or any initials) is a comment made by a specific person, sometimes targeting a specific person (or future me!).

## Variables

I always name my variables with underscores and I tend to give them long names.
The idea being that we are not restricted by the number of characters! (we don't use 8 bits compilers anymore...)

```{r}
## Some naming
this_is_a_variable <- 1
```

When it comes to variable name, I find the more descriptive in terms of code interpretation the better:

```{r}
## Some obvious variable names
my_integer <- 1
my_matrix <- matrix(NA)
matrix_rows <- nrow(my_matrix)
matrix_row_names <- rownames(my_matrix)
```

## Functions

On the other hand, functions are dot separated.
I tend to use the same long verbose names as for variables.

```{r}
## One function
my.function <- function() {
    return(NULL)
}
```

Again, the more descriptive the better

```{r}
## Some nice obvious function names
do.null <- function() {
    return(NULL)
}
add.values <- function(x, y) {
    return(x + y)
}
```

When designing functions for `apply` class functions, I often name them following the functions.
For example

```{r}
## A function to be passed to a lapply
square.values.lapply <- function(x) {
    return(x^2)
}
lapply(list(1,2,3), square.values.lapply)

add.values.mapply <- function(x, y) {
    return(x + y)
}
mapply(add.values.mapply, list(1,2,3), list(1,2,3))
```

## Loops arguments

Although I actively try to prefer using `apply` class functions, I sometime use `for` class loops for specific tasks.
When that happens, I specifically name the variables rather than give them indices names:


```{r}
## A complex loop!
for(one_integer in 1:3) {
    print(one_integer)
}
```

This can be specifically useful in nested loops (which should be avoided!):

```{r}
## A simple square matrix
simple_matrix <- matrix(1:4, 2, 2)

## A nested loop
for(row in 1:nrow(simple_matrix)) {
    for(column in 1:ncol(simple_matrix)) {
        print(simple_matrix[row, column])
    }
}
```

## Logicals

I tend to call logicals directly as conditions

```{r}
## Setting a condition to TRUE
condition <- TRUE

## If the condition is true
if(condition) {
    ## Print the condition (TRUE)
    print(condition)
} else {
    ## Print the condition (FALSE)
    print(condition)
}
```

On the opposite, if the condition should not be met, I will use it's inverse as a condition (`!condition`).
I find this works elegantly with the loop structure described above:

```{r}
## Set a counter
counter <- 1

## Setting the condition to FALSE
condition <- FALSE

## A conditional loop
while(!condition) {
    ## Add another condition
    if(counter >= 4) {
        ## Change the condition
        condition <- TRUE
    } else {
        ## Print the count
        print(counter)
    }
    ## Increment a counter
    counter <- counter + 1
}
```
<!-- 

## Messages


```{r}
# message(paste(match_call$object, " is not good"), .call = FALSE)
```


## Path and folders

```
ThisIsAFolder
```

```
this_is_a_file
```

## Objects and methods

```{r}
my_object <- 1
class(my_object) <- "myClass"
```

 -->